---
title: KUL Faculty Social Sciences MethLab report
author: Amandine Larusse^[[Amandine Lerusse](https://soc.kuleuven.be/io/english/staff/00119302) is a Ph.D candidate at the Public Governance Institute, KU Leuven. Email:\hspace{0.1cm} amandine.lerusse@kuleuven.be], Luca Carbone^[[Luca Carbone](https://www.lucacarbone.com) is an Ph.D candidate at the School for Mass Communication Research, KU Leuven. Email:\hspace{0.1cm} lucacarbone.lc@gmail.com], Alberto Stefanelli^[[Alberto Stefanelli](https://albertostefanelli.com/) is an FWO Ph.D Fellow at the Institute for Social and Political Opinion Research, KU Leuven. Email:\hspace{0.1cm} alberto.stefanelli@kuleuven.be]
knit: (function(inputFile, encoding) { 
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(dirname(inputFile), output_dir="./docs/report.html")) })
bibliography: /Users/serg/Library/Mobile Documents/com\~apple\~CloudDocs/academia/library.bib
link-citations: true
urlcolor: blue
abstract: \noindent \singlespacing Methlab survey report
output: 
    # pdf_document:
    #   number_sections: true
    #   #toc: true
    #   fig_caption: yes
    #   fig_width: 7
    #   fig_height: 7
    #   keep_tex: no
    html_document
    # word_document:
    #   reference_docx: mystyles.docx
    #   toc: true
    #   fig_caption: true
header-includes:
  - \usepackage{fancyhdr}
  # - \usepackage{longtable}
  # - \usepackage{booktabs}
  # - \usepackage{dcolumn}
  # - \usepackage{threeparttable}
  - \fancyhf{}
  - \fancyhead[RO]{}
  - \fancyhead[RE]{Alberto Stefanelli}
  # - \fancyfoot[C]{\thepage}
  # - \pagestyle{fancy}
  # - \usepackage{setspace}\doublespacing
  # - \renewcommand{\headrulewidth}{0.4pt}
  # - \renewcommand{\footrulewidth}{0pt}
  - \usepackage{float}
  #- \usepackage{sidewaystable}
  # - \DeclareUnicodeCharacter{FB01}{fi}
  - \usepackage{setspace}\doublespacing
  - \usepackage{lscape}
  - \newcommand{\blandscape}{\begin{landscape}}
  - \newcommand{\elandscape}{\end{landscape}}
  - \usepackage{colortbl}


### BLUE LINK 
### GRAMMAR CECK
### FIGURE TOC
### APPENDIX AFTER BIB 
---

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='hide'}
source("./script_analysis.r",local = knitr::knit_global())
```

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='hide'}
#install.packages('wordcountaddin')
word_count <- wordcountaddin::word_count("report.Rmd")
```

|                                                    |
|:--------------------------------------------------:|
| `r paste("Word Count (WO references)",word_count)` |

# Intro

# Method background of our sample 



```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

print(survey_data_labels %>% select(Q3) %>% gtsummary::tbl_summary())

```

# Interest in Training

## Interest in Qualtitative courses 


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

for (i in seq(interested_quali)){
q <- names(survey_data)[interested_quali[[i]]]
n <- quali_questions_labels[[i]]
print(gtsummary::tbl_cross(survey_data_labels, row=q, col=Q3, percent="row",
                label = list(q ~ n )
) %>% as_gt() )
  
}


```{r Interests qualitative courses, echo=FALSE, fig.cap="Interests qualitative courses", out.width = '100%'}
knitr::include_graphics("quali_pref.tiff")
```

```


## Interest in Quantitative courses 


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

for (i in seq(interested_quanti)){
  q <- names(survey_data)[interested_quanti[[i]]]
  n <- quanti_questions_labels[[i]]
  print(tbl_cross(survey_data_labels, row=q, col=Q3, percent="row",
                  label = list(q ~ n )
  ))

}



```

  
## Interest in other training activites 

```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

for (i in seq(training)){
q <- names(survey_data)[training[[i]]]
n <- training_questions_labels[[i]]
print(gtsummary::tbl_cross(survey_data_labels, row=q, col=Q3, percent="row",
                label = list(q ~ n )
) %>% as_gt() )
  
}




```
  

## Interest in other Methlab activites 


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

print(survey_data_labels %>% select(Q13) %>% gtsummary::tbl_summary(label = list(Q13 ~ "Interested in joining a 'PhD soup'"
)))


```



```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

print(survey_data_labels %>% select(Q15) %>% gtsummary::tbl_summary(label = list(Q15 ~ "Interested in a methods-related newsletter")))


```

# Expertise in Methods

## Knowledge in Qualtative courses 


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

for (i in seq(expert_quali)){
q <- names(survey_data)[expert_quali[[i]]]
n <- quali_questions_labels[[i]]
print(gtsummary::tbl_cross(survey_data_labels, row=q, col=Q3, percent="row",
                label = list(q ~ n )
) %>% as_gt() )
  
}




```

  
## Knowledge in Quantitative courses 


```{r echo=FALSE, message=FALSE, warning=FALSE, cache=FALSE, results='asis'}

for (i in seq(expert_quanti)){
q <- names(survey_data)[expert_quanti[[i]]]
n <- quanti_questions_labels[[i]]
print(gtsummary::tbl_cross(survey_data_labels, row=q, col=Q3, percent="row",
                label = list(q ~ n )
) %>% as_gt() )
  
}




```




